---
pagetitle: "CAMPSIS Miscellaneous"
date: ""
author: ""
output: github_document
always_allow_html: true
---

# campsismisc

## Forest plots

Assume the following estimated 2-compartment model:

```{r, message=FALSE, warning=FALSE}
library(campsismisc)
library(progressr)

model <- read.campsis("tests/testthat/campsis_models/metaboliser_effect_on_cl/")
model
```

This model contains:

- a metabolism effect on the clearance: `THETA_METAB_CL`
- allometric scaling on central and peripheral volumes with a fixed exponent of 1
- a variance-covariance matrix

### Configure your simulation settings

```{r, message=F}
# Configure hardware
settings <- Settings(Hardware(cpu=8, replicate_parallel=TRUE))
dest <- "mrgsolve" # Much faster than RxODE
```


### Effect of metabolism effect and weight on model parameters

Let's show how the metabolism effect and the weight influence the clearance or the volume. This can be achieved as follows:

```{r, message=F}
outputs <- OATOutputs() %>%
  add(ModelParameterOutput("CL")) %>%
  add(ModelParameterOutput("VC"))

fp <- ForestPlot(model=model, outputs=outputs, replicates=100, dest=dest, settings=settings) %>%
    add(CategoricalLabeledCovariate(name="METAB", default_value=0, label="Metaboliser", categories=c(Slow=0, Fast=1))) %>%
    add(LabeledCovariate(name="WT", default_value=70, label="Weight", unit="kg")) %>%
    add(ForestPlotItem(Covariate("METAB", 0))) %>%
    add(ForestPlotItem(Covariate("METAB", 1))) %>%
    add(ForestPlotItem(Covariate("WT", 60))) %>%
    add(ForestPlotItem(Covariate("WT", 80)))

fp <- with_progress({fp %>% prepare()})
```

The forest plot for clearance can be otained as follows (use `index=1`):

```{r fp_metabolism_effect_on_cl, fig.align='center', fig.height=4, fig.width=8, message=F}
fp %>% getForestPlot(index=1) +
  ggplot2::scale_y_continuous(breaks=c(0.7,0.8,1,1.25,1.4), limits=c(0.5, 1.5))
```

Similarly, the forest plot for volume can be obtained as follows (use `index=2`):

```{r fp_metabolism_effect_on_vc, fig.align='center', fig.height=4, fig.width=8, message=F}
fp %>% getForestPlot(index=2) +
  ggplot2::scale_y_continuous(breaks=c(0.7,0.8,1,1.25,1.4), limits=c(0.5, 1.5))
```

### Effect of metabolism and weight on PK metrics

Let's show how the metabolism effect and the weight influence PK metrics. For that, we need to create first a dataset. Assume we are interested to compute AUC/Cmax on day 1 and day 7. We give the drug every day and we observe on day 1 and day 7.

```{r}
dataset <- Dataset(1) %>%
    add(Infusion(time=0, amount=1000, compartment=1, ii=24, addl=6)) %>%
    add(Observations(times=c(0:24, 144:168)))
```

Instead of creating a `ModelParameterOutput` object, we create a `NcaMetricOutput` for each metric we want to compute (by referring to the proper `campsisnca` metric). Each output is added to the list of outputs as follows:

```{r}
outputs <- OATOutputs() %>%
  add(NcaMetricOutput(AUC(variable="CONC"), filter=~campsisnca::timerange(.x, min=0, max=24))) %>%
  add(NcaMetricOutput(AUC(variable="CONC"), filter=~campsisnca::timerange(.x, min=144, max=168), suffix="Day 7")) %>%
  add(NcaMetricOutput(Cmax(variable="CONC"), filter=~campsisnca::timerange(.x, min=0, max=24))) %>%
  add(NcaMetricOutput(Cmax(variable="CONC"), filter=~campsisnca::timerange(.x, min=144, max=168), suffix="Day 7"))
```

A forest plot object can be instantiated and run as follows:

```{r, message=F}
fp <- ForestPlot(model=model, dataset=dataset, outputs=outputs,
                 replicates=100, dest=dest, settings=settings) %>%
    add(CategoricalLabeledCovariate(name="METAB", default_value=0, label="Metaboliser", categories=c(Slow=0, Fast=1))) %>%
    add(LabeledCovariate(name="WT", default_value=70, label="Weight", unit="kg")) %>%
    add(ForestPlotItem(Covariate("METAB", 0))) %>%
    add(ForestPlotItem(Covariate("METAB", 1))) %>%
    add(ForestPlotItem(Covariate("WT", 60))) %>%
    add(ForestPlotItem(Covariate("WT", 80)))

fp <- with_progress({fp %>% prepare()})
```

We can look at AUC day 1 by doing:

```{r fp_metabolism_effect_on_auc_d1, fig.align='center', fig.height=4, fig.width=8, message=F}
fp %>% getForestPlot(index=1) +
  ggplot2::scale_y_continuous(breaks=c(0.7,0.8,1,1.25,1.4), limits=c(0.5, 1.5))
```

If we are interested to see the absolute change in AUC, argument relative can be set to FALSE as follows.

```{r fp_metabolism_effect_on_auc_d1_absolute, fig.align='center', fig.height=4, fig.width=8, message=F}
fp %>% getForestPlot(index=1, relative=FALSE)
```

To look at AUC on day 7, we proceed as follows:

```{r fp_metabolism_effect_on_auc_d7, fig.align='center', fig.height=4, fig.width=8, message=F}
fp %>% getForestPlot(index=2) +
  ggplot2::scale_y_continuous(breaks=c(0.7,0.8,1,1.25,1.4), limits=c(0.5, 1.5))
```

Again, we can look at the absolute values.

```{r fp_metabolism_effect_on_auc_d7_absolute, fig.align='center', fig.height=4, fig.width=8, message=F}
fp %>% getForestPlot(index=2, relative=FALSE)
```

Let's produce one more plot with Cmax on day 1.

```{r fp_metabolism_effect_on_cmax_d1, fig.align='center', fig.height=4, fig.width=8, message=F}
fp %>% getForestPlot(index=3) +
  ggplot2::scale_y_continuous(breaks=c(0.7,0.8,1,1.25,1.4), limits=c(0.5, 1.5))
```

And a final one with Cmax on day 7.

```{r fp_metabolism_effect_on_cmax_d7, fig.align='center', fig.height=4, fig.width=8, message=F}
fp %>% getForestPlot(index=4) +
  ggplot2::scale_y_continuous(breaks=c(0.7,0.8,1,1.25,1.4), limits=c(0.5, 1.5))
```

Finally, you need to know that you can combine model parameter ouputs together with NCA metric outputs, if you want! This will make your simulations even faster. In that specific case, Campsis will check that your model parameters do not vary over time (since several observations are provided in the dataset).

## OAT-method based sensitivity analysis

### Effect of model parameters on PK metrics

Assume the same 2-compartment model. Let's see how the model parameters influence AUC or Cmax if they are multiplied by two. This can be achieved with a one-at-a-time (OAT)-method-based sensitivity analysis. Most of the time, these analyses are done without parameter uncertainty (replicates=1, by default) and represented with tornado plots, as shown below. However if parameter uncertainty is used, you can still call `getForestPlot()` on this new type of object.

```{r sensibility_analysis_auc_example, fig.align='center', fig.height=3, fig.width=8, message=F}
outputs <- OATOutputs() %>%
  add(NcaMetricOutput(AUC(variable="CONC"))) %>%
  add(NcaMetricOutput(Cmax(variable="CONC")))

dataset <- Dataset(1) %>%
  add(Infusion(time=0, amount=1000, compartment=1)) %>%
  add(Observations(times=seq(0, 24, by=0.1))) %>%
  add(Covariate("METAB", 0)) %>%
  add(Covariate("WT", 70))

object <- SensitivityAnalysis(model=model, dataset=dataset, outputs=outputs) %>%
  add(LabeledParameters(c(DUR="Duration", VC="Central volume", VP="Peripheral volume", Q="Inter-compartmental\nclearance", CL="Clearance"))) %>%
  add(SensitivityAnalysisItem(Change("DUR", up=2, down=2))) %>%
  add(SensitivityAnalysisItem(Change("VC", up=2, down=2))) %>%
  add(SensitivityAnalysisItem(Change("VP", up=2, down=2))) %>%
  add(SensitivityAnalysisItem(Change("Q", up=2, down=2))) %>%
  add(SensitivityAnalysisItem(Change("CL", up=2, down=2)))

object <- object %>% prepare()
object %>% getTornadoPlot(index=1)
```

Absolute values may also be shown:

```{r sensibility_analysis_auc_example_absolute, fig.align='center', fig.height=3, fig.width=8, message=F}
object %>% getTornadoPlot(index=1, relative=FALSE)
```

Cmax can also be shown using `index=2`.

```{r sensibility_analysis_cmax_example, fig.align='center', fig.height=3, fig.width=8, message=F}
object %>% getTornadoPlot(index=2)
```

```{r, echo=FALSE, message=F, results='hide'}
setupPlanSequential()
```


